|

### 2024-08-20 reproducibility/manuscript/manuscript.qmd
docs(manuscript): update text
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

>>>>

In conclusion, Pyro-Velocity provides the first probabilistic, interpretable,
end-to-end Bayesian inference framework for RNA Velocity that learns cell
dynamics and recovers cell fate from multimodal raw read counts.  This approach
provides uncertainty estimations of cell fate trajectories and novel
visualization approaches to mitigate false discoveries. Pyro-Velocity recovered
shared time and vector fields that are recapitulated in true developmental order
and outperformed state-of-the-art methods like Cytotrace and scVelo
([@suppfig-lineage-tracing]a).

# Software availability

We developed our Pyro-Velocity models with Pyro (version 1.6.0) probabilistic
programming language and PyTorch (version 1.8.1). Pyro-Velocity source code is
available at <https://github.com/pinellolab/pyrovelocity>. The version of
Pyro-Velocity (v0.1.0) used to generate the results presented in this manuscript
has been deposited on Zenodo: <https://zenodo.org/record/7072876#.Yx-2e-zMLxg>.

# Data availability

All the data presented in this manuscript were collected from previously
published studies. The fully mature PBMC, pancreas datasets are downloaded and
loaded through the scVelo using `scvelo.datasets.pancreas()`, and
`scvelo.datasets.pbmc68k()`. The LARRY inDrop sequencing data was processed by
the LARRY authors using dropEst [@Petukhov2018-nr] and velocyto. This dataset
can be accessed at
<https://figshare.com/articles/dataset/larry_invitro_adata_sub_raw_h5ad/20780344>.

# Acknowledgments

This project has been made possible in part by grant number 2022-249212 from
the Chan Zuckerberg Initiative DAF, an advised fund of Silicon Valley Community
Foundation. L.P. received support from the U.S. NIH (R35 HG010717) and Silicon
Valley Community Foundation (2022-249212). D.M.L is supported by R01CA226926,
R01 CA215118, R01CA154923, R24 OD031955, CureSearch Acceleration Initiative, and
the MGH Scholars Award. We thank the Pinello and Langenau labs members for
helpful discussions.

# Author contributions

L.P., Q.Q., and E.B. conceived the work. Q.Q. and E.B created the software. Q.Q.
analyzed the data, and prepared the figures and tables. L.P and D.L. supervised
the project.  L.P., D.L., E.B., G.L.M helped in designing experiments and
analyses.  All the authors contributed to the writing of the manuscript.
